Analysis

### 2018-06-25 reports/analysis_pilot.Rmd
add analysis per each category
currently on one subject only

>>>>

# Analysis categ

data_pth <- here::here("data", "results", "categ")

df <- df %>%
  mutate(target_image = paste0("image",target_position),
         correct = as.numeric(target_image == mouse.clicked_name),
         category_type = if_else(category %in% c("desert", "waves", "coast", "underwater", "iceberg","field","garden","cavern","beach","canyon","mountainwhite","woods"),"natural","manmade"))

# Desc stat

```{r}
df %>% 
  group_by(quintile) %>% 
  summarize(m = mean(correct) %>% round(2), sd = sd(correct) %>% round(2))

df %>% 
  group_by(category_type) %>% 
  summarize(m = mean(correct) %>% round(2), sd = sd(correct) %>% round(2))

# Visualize

```{r}
df %>% ggplot(aes(x = quintile, y = correct)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  ylim(0,1)+
  theme(aspect.ratio = 1) +
  geom_hline(yintercept = 1/9) 
```

# Analysis all
